Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-19 tex/paper1/paper1.tex
more edits to the paper

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\caption{Geometric mean of the \protect\Fpa\ (black solid line) in
  each of the four regions studied in AIA 171\AA\ (left column) and
  AIA 193\AA\ (right column).  Also shown are the posterior mean and
  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (blue and red
  lines respectively; see Section \ref{sec:anal} and Appendix
  \ref{sec:app:ind} for more detail).  The AIC and BIC describing the
  preference for model over the other is also indicated in each plot.
  The two components to Model 2, $P_{1}(\nu)$ and $G(\nu)$ are also
  shown in green; the location of the maximum of their ratio is
  indicated by the green dotted line.  Model fit parameter values and
  their 68\% credible intervals are quoted in Table
  \ref{tab:parameters}.}
\label{fig:fit171193}
\end{figure}

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{\PL} & \multicolumn{3}{c}{lognormal} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$}      &
\colhead{$\delta$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{}          & 
\colhead{}      & 
\colhead{}      &
\colhead{} &
\colhead{(mHz)}      &
\colhead{(decades of frequency)}\\
}
\startdata
loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{+0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.26^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
                & & & & & & & \\

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions (Figure
\ref{fig:fit171193}), and compared to decide which model best
describes the data. The details of the model fitting process are
described in \ref{sec:app:ind}.

@@

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt(2\pi\sigma^{2}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$,
$N_{f}$ is the number of Fourier frequencies, and $\sigma_{j}$ is the
normal distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution, and are given
in Table \ref{tab:priors}.  Each MCMC chain that was run took 100,000
samples, with burn-in assumed to be at 50,000 samples.  The chain is
thinned by taking every fifth element in the chain, forming the final
sample from which the parameter estimates and their uncertainties are
calculated.

\begin{deluxetable}{cc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & $4.5 \times 10^-5 \rightarrow 22026$ &  $4.5 \times 10^-5 \rightarrow 22026$\\
$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
$C$ & $2.1 \times 10^-9 \rightarrow 22026$  & $2.1 \times 10^-9 \rightarrow 22026$  \\
$\alpha$  & not applicable & $2.1 \times 10^-9 \rightarrow 148$ \\
$\beta$ & not applicable  & $1 - 10$ \\
$\delta$ & not applicable & $0.001\rightarrow 3$ \\
\enddata
\end{deluxetable}

>>>>

\begin{figure}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\caption{Geometric mean of the \protect\Fpa\ (black solid line) in
  each of the four regions studied in AIA 171\AA\ (left column) and
  AIA 193\AA\ (right column).  Also shown are the posterior mean and
  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (blue and red
  lines respectively; see Section \ref{sec:anal} and Appendix
  \ref{sec:app:ind} for more detail).  The AIC and BIC describing the
  preference for model over the other is also indicated in each plot.
  The two components to Model 2, $P_{1}(\nu)$ and $G(\nu)$ are also
  shown in green; the location of the maximum of the
  $G(\nu)/P_{1}(\nu)$ ratio is indicated by the green dotted line.
  Model fit parameter values and their 68\% credible intervals are
  quoted in Table \ref{tab:parameters}.}
\label{fig:fit171193}
\end{figure}

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & \multicolumn{3}{c}{lognormal $G(\nu)$} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$}      &
\colhead{$\delta$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{}          & 
\colhead{}      & 
\colhead{}      &
\colhead{} &
\colhead{(mHz)}      &
\colhead{(decades of frequency)}\\
}
\startdata
loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{+0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.26^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
                & & & & & & & \\

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions (Figure
\ref{fig:fit171193}), and compared to decide which model best
describes the data. The details of the model fitting process are
described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
restricted by permitting $\beta$ to vary in the range $1-10$ mHz only.
This restriction, which is imposed in the fitting process (see Section
\ref{{sec:app:ind}), arises from the observations of significant
  wavelet power in the period rangs 200 - 600 seconds as found by
  \cite{2003ApJ...595L..63D}.

@@

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt(2\pi\sigma^{2}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$,
$N_{f}$ is the number of Fourier frequencies, and $\sigma_{j}$ is the
normal distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution, and are given
in Table \ref{tab:priors}.  Each MCMC chain that was run took 100,000
samples, with burn-in assumed to be at 50,000 samples.  The chain is
thinned by taking every fifth element in the chain, forming the final
sample from which the parameter estimates and their uncertainties are
calculated.
\begin{deluxetable}{cc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & $4.5 \times 10^-5 \rightarrow 22026$ &  $4.5 \times 10^-5 \rightarrow 22026$\\
$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
$C$ & $2.1 \times 10^-9 \rightarrow 22026$  & $2.1 \times 10^-9 \rightarrow 22026$  \\
$\alpha$  & not applicable & $2.1 \times 10^-9 \rightarrow 148$ \\
$\beta$ & not applicable  & $1 - 10$ \\
$\delta$ & not applicable & $0.001\rightarrow 3$ \\
\enddata
\end{deluxetable}
